GVN-hoist: hoisting expressions from control flow

### 2016-08-04 hoist.tex
make it compile

@@

@@

\begin{section}

@@

\begin{program}
float foo(float d, float min, float max, float a)
{
  float tmin;
  float tmax;

  float inv = 1.0f / d;
  if (inv >= 0) {
    tmin = (min - a) * inv;
    tmax = (max - a) * inv;
  } else {
    tmin = (max - a) * inv;
    tmax = (min - a) * inv;
  }
  return tmax + tmin;
}

\end{program}

@@

But if we hoist the computation of tmax and tmin outside the
conditionals, the C code version would look like this:
\begin{program}
float foo(float d, float min, float max, float a)
{
  float tmin;
  float tmax;

@@

\end{program}

@@

\begin{program}
float foo(float d, float min, float max, float a)
{
  float tmin;
  float tmax;

@@

  return tmax' + tmin';
}
\end{program}

@@

\end{section}

>>>>

\documentclass{sig-alternate}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{graphviz}
\usepackage{auto-pst-pdf}
\usepackage{etoolbox}
\usepackage{flushend}
\usepackage{needspace}

\makeatletter
\preto{\@verbatim}{\topsep=1pt \partopsep=0pt}
\makeatother

\pagenumbering{arabic}

\begin{document}
\def \SCoP {SCoP}
\def \GCC {GCC}
\def \LLVM {LLVM}
\def \SESE {SESE}
\def \CFG {CFG}
\def \SSA {SSA}
\def \scev {scev}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\title{GVN-hoist: hoisting expressions from control flow}

\toappear{
   \hrule \vspace{5pt}
   LLVM-dev 2016
}
\numberofauthors{2}

\author{
\alignauthor
Aditya Kumar\\
       \affaddr{Samsung Austin R\&D Center}\\
       \email{aditya.k7@samsung.com}
\alignauthor
Sebastian Pop\\
       \affaddr{Samsung Austin R\&D Center}\\
       \email{s.pop@samsung.com}
}

\maketitle
\begin{abstract}
Code hoisting does not remove redundancies by itself but it enables
removal of redundancies by other passes.  e.g., Enable inlining.
\end{abstract}

@@

graph algorithms \cite{tarjan},
SSA \cite{cytron}
GVN \cite{rosen1988global,click1995global}
CFG, DOM \cite{dragonbook}
SESE, SEME \cite{sese}

@@

@@

\begin{verbatim}
float foo(float d, float min, float max, float a)
{
  float tmin;
  float tmax;

  float inv = 1.0f / d;
  if (inv >= 0) {
    tmin = (min - a) * inv;
    tmax = (max - a) * inv;
  } else {
    tmin = (max - a) * inv;
    tmax = (min - a) * inv;
  }
  return tmax + tmin;
}
\end{verbatim}

@@

But if we hoist the computation of tmax and tmin outside the
conditionals, the C code version would look like this:
\begin{verbatim}
float foo(float d, float min, float max, float a)
{
  float tmin;
  float tmax;

@@

\end{verbatim}

@@

\begin{verbatim}
float foo(float d, float min, float max, float a)
{
  float tmin;
  float tmax;

@@

  return tmax' + tmin';
}
\end{verbatim}

@@

\bibliographystyle{abbrv}
{\small
\bibliography{Bibliography}
}
\end{document}
